Continous time Markov chain models; \\ extension, simulation and visualisation

### 2015-02-11 chapters/chapter01.tex
response

Both the rate of evolution $r$ and the unobserved heights $T_{0},T_{6},T_{7},T_{8}$ are estimated from the molecular sequence data, with the constraint that the heights are proportional to their sampling time and teh ratio of this proportionality being $r$.
}

>>>>

Both the rate of evolution $r$ and the unobserved heights $T_{0},T_{6},T_{7},T_{8}$ are estimated from the molecular sequence data, with the constraint that the heights are proportional to their sampling time and the ratio of this proportionality being $r$.
}
